---
title: "行動力"
---

<!-- Smooth scroll: conflicts with tabset -->

<script type="text/javascript" src='./smooth_scroll.js'></script>

<!-- Popup Modal-->
<script type="text/javascript">
$(window).on('load',function(){
$('#first_modal').modal('show');
});</script>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	dev='svg',
	fig.dim = c(5.5, 3.5)  # (width, height)
)
source("bootstrap_fc.R")
```


## Section 1

[Link To 第三段 MD](#sec3){.btn .btn-success  role="button"}

<a onclick="popupCenter('https://docs.google.com/spreadsheets/d/1ufuzTL9VCxdvX1QeFQcMGxYbEMq1ZEWVht3CEDpXBmc/edit?usp=sharing', 'myPop1',400,400);" href="javascript:void(0);">CLICK TO OPEN POPUP</a>
<script>
function popupCenter(url, title, w, h) {
var left = (screen.width/2)-(w/2);
var top = (screen.height/2)-(h/2);
return window.open(url, title, 'toolbar=no, location=no, directories=no, status=no, menubar=no, scrollbars=no, resizable=no, copyhistory=no, width='+w+', height='+h+', top='+top+', left='+left);
}
</script>
<br>

```{r}
# Button trigger modal
button_bs("Launch", data_toggle="modal", data_target="#first_modal")

modal_body <- button_bs("Take Test", class = "warning", data_toggle = "modal", data_target = "#psytest")

modal_body2 <- button_bs("Proceed", class = "success pull-right", data_dismiss = "modal")

# Modal
modal(modal_header="Header", id="first_modal", modal_body = modal_body, modal_body2 = modal_body2, size = "modal-sm")

# iframe for Google Form
iframe <- HTML('<iframe src="https://docs.google.com/forms/d/e/1FAIpQLSeE-ke7yhlU3XRDIhw7vRL-mnYLi-jTOYF8Pz4ZLINjV53z2A/viewform?embedded=true" style="position: relative; height: 300px; width: 100%;" frameborder="0" marginheight="0" marginwidth="0">載入中…</iframe>')

viewResult <- button_bs("Result", data_toggle="modal", data_target="#response", class="primary pull-left")

modal(id="psytest", modal_header = "行動力量表", modal_body=iframe, modal_footer=viewResult)

# iframe for response google sheet
iframe2 <- HTML('<iframe  width="100%" height="200px" frameborder="0" scrolling="no"  src="https://docs.google.com/spreadsheets/d/e/2PACX-1vQz4zjZfhWBYYRuW2Zhhx-sXvnlrS6vpvcgP0cJPdvsQI-6eKggXmpaWbu4dgbMQgcOHv0NQxL8a_K_/pubhtml?gid=0&amp;single=true&amp;widget=false&amp;chrome=false&amp;headers=false"></iframe>')

# modal: response
modal(id="response", modal_header = "分數", modal_body=iframe2, size="modal-sm")
```


<br>

```{r}
button_bs("Launch widget", data_toggle="modal", data_target="#htmlwidget")
```

<br>

<div id="htmlwidget" class="modal fade" role="dialog" tabindex="-1">
<div class="modal-dialog" role="document">
<div class="modal-content">
<div class="modal-header">
<button type="button" class="close" data-dismiss="modal">&times;</button>
<h4 class="modal-title">行動力量表</h4>
</div>
<div class="modal-body">

<div class="tab-content">
```{r}
library(heatmaply)
source("./rscript/corr_matrix.R", encoding = "utf-8")
hm
```
</div>

<div class="modal-footer">
<button type="button" class="btn btn-default" data-dismiss="modal">Close</button>
</div>
</div>
</div>
</div>
</div>


<br><br><br><br><br><br><br>

## 中文{#chi .tabset}

<div class="alert alert-success" role="alert">
This is success
</div>

<br>

### Tab1
This is Tab 1

### Tab 2
This is Tab 2



## 第三段{#sec3}


<div id="pad">
```{r}
button_bs("See Collapse", class="info", data_toggle="collapse", aria_expanded="false", aria_controls="collapseExample", data_target = "#collapseExample")
```
</div>

```{r}
HTML('
<div class="collapse" id="collapseExample">
  <div class="alert alert-info">
    Collasped Text
  </div>
</div>')
```


<div class="panel panel-success">

<div class="panel-heading">
<h3 class="panel-title">Panel title</h3>
</div>

<div class="panel-body">
Panel content
</div>
  
</div>
<br><br><br><br><br><br><br><br><br>
