---
title: "Grid System"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	dev='svg'
	# fig.dim = c(3.5, 3.5)  # (width, height)
)
library(knitr)
library(kableExtra)
htmlwidgets::sizingPolicy(
    browser.fill=TRUE
)
source("bootstrap_fc.R")
```



<div class="container-fluid">
<div class="row  alert alert-success">

<div class="col-xs-12 col-md-4">
This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah...
</div>

<div class="col-xs-6 col-md-4">
```{r}
library(ggplot2)
p <- ggplot(iris) + geom_point(aes(x=Sepal.Length, y=Petal.Length, color=Species))
p
```
</div>

</div>
</div>



<div class="container-fluid">
<div class="row  alert alert-info">

<div class="col-xs-6 col-sm-4">
```{r}
p
```
1 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

<div class="col-xs-6 col-sm-4">
```{r}
p
```
2 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

<div class="col-xs-6 col-sm-4">
```{r}
p
```
3 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

</div></div>


<div class="container-fluid">
<div class="row  alert alert-info">

<div class="col-xs-6 col-md-3">
```{r}
p
```
3 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

<div class="col-xs-6 col-md-3">
```{r}
p
```
3 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

<div class="col-xs-6 col-md-3">
```{r}
p
```
3 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

<div class="col-xs-6 col-md-3">
```{r}
p
```
3 This is some text. blah blah blah blah blah...This is some text. blah blah blah blah blah blah blah blah blah blah...blah blah blah blah blah...blah blah blah blah blah...</div>

</div></div>