---
title: "Analysis Documentation"
output: 
    html_document:
        toc: true
        number_sections: true
css: /Users/user/local_depend/style_sheets/style.css
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, comment="")
library(DiagrammeR)
```

```{r}
library(DiagrammeR)

grViz("
digraph { //directed graph
      graph [layout = dot]  //layout = dot|neato|twopi|circo|fdp
      rankdir=TB    // LR: Left to Right

      node [shape = oval,
      style = filled,
      color = orange]
      
      node [fillcolor = orange1] // Code: input & output data
      a1 [label = 'data_import_cleaning.R']
      a2 [label = 'preprocess.R']
      a3 [label = 'item_analysis.R']

      node [fillcolor = gray, shape = box]  //data
      d_ori1 [label = '問卷題目.xlsx' fillcolor = YellowGreen]
      d_ori2 [label = 'psy_test.csv' fillcolor = YellowGreen]
      d1 [label = 'item.csv' fillcolor = YellowGreen]

      d2 [label = 'psy_test_parsed.rds']
      d3 [label = 'item_construct.rds']
      d4 [label = 'psy_test_analy.rds']
      d5 [label = 'item_construct_conNum.rds']
      d6 [label = 'psy_test_filtered.rds']
      
      node [fillcolor = OrangeRed shape = oval,]  // Code: input data only
      p1 [label = 'plotting.R']
      p2 [label = 'corr_matrix.R']
      p3 [label = 'plotting_descri.R']
      anova [label = 'anova.R']
      
      
      
      edge [color = grey, arrowtail = none]
      d_ori1 -> d1
      
      {d1 d_ori2} -> a1
      a1 -> {d2 d3}
      
      {d2 d3} -> a2
      a2 -> {d4 d5}
      
      {d4 d5} -> a3
      a3 -> d6
      
      d4 -> {p1 p2}
      d5 -> {p1 p2 p3 anova}
      d6 -> {p1 p2 p3 anova}
      }")
```


Data
===============================
Parent Data
-------------------------------
- `psy_test.csv`: Original Data, dowloaded from Google Form Directly

- `item.csv`: Generated from `問卷題目.xlsx` **manually**, contain information about:
	1. item number(coded for analysis)
	2. item construct(Ch & Eng)
	3. item type: whether need **reverse-scoring**
	4. question number: original item number in Google Form questionaire
	5. item content: questions in Google Form questionaire

------------------------------------------------------

R script
================================

## `data_import_cleaning.R`
- Input
	1. `psy_test.csv`
	2. `item.csv`

- Output
	1. `psy_test_parsed.rds`
	2. `item_construct.rds`

Map original variable names of `psy_test.csv`(Chinese) to new variable names with `var_info`(output as `item_construct.rds`).

Convert variable names of `psy_test.csv`(Chinese) to English.

Standardize and factorize:
- **gender**, **grade**, **college**, **department**(categorized as well)

Remove duplicated & NA Rows

---------------------------------

## `preprocess.R`

### Data Inputs & Outputs
- Input
	1. `psy_test_parsed.rds`
	2. `item_construct.rds`

- Output
	1. `psy_test_analy.rds`
	2. `item_construct_conNum.rds`

### Description
**Output:** `psy_test_analy.rds`

- Reverse Scoring

- Calculate **total & construct scores**
	- Add **total & construct scores** as new variables to psy_test(`psy_test_parsed.rds`)

**Output:** `item_construct_conNum.rds`

- Add **construct-number** as new variable to var_info(`item_construct.rds`)
	- Form: AT-01

------------------------------------

## `item_analysis.R`

### Data Inputs & Outputs
- Input
	1. `psy_test_analy.rds`
	2. `item_construct_conNum.rds`

- Output
	1. `psy_test_filtered.rds`

### Description
`psy_test_f`: Filter out **first grade** & **Fake-good scores over 18($\geqslant 18$)**.

Correlation between constructs & Total score(`construct_cor_mt`)

#### Item Indices(`stats`)
- Cronbach's Alpha
	1. All Constucts
	2. Whole Questionare
	3. All Items(`item_stats$alpha`)
		- Alpha of the construct that the item belongs to **with the item itself removed**.
		- To see whether alpha increased(compared to 1. `item_stats$alpha_ori`) after removal of the item.

- Items' correlations with their constructs(`item_stats$corr`)

- Item, Construct, & Total scores' **mean**, **std**, **skewness**, **Difference in Scores between Upper 27.5% and Lower 27.5% groups**(group defined by total score)


## `plotting.R`

### Data Inputs & Outputs
- Input:
	1. `psy_test_analy.rds`
	2. `psy_test_filtered.rds`
	3. `item_construct_conNum.rds`

### Description
Visualize **effect of fake-good cutoffs**, **distributions of items**

1. fake-good cutoffs
	- corr. between Fk & other constructs + total test score
	- visualized as line chart(x = cutoff score, y = correlation)

2. distributions of items
	- bar chart: x = score, y = freq

## `corr_matrix.R`

### Data Inputs & Outputs
- Input:
	1. `psy_test_analy.rds`
	2. `psy_test_filtered.rds`
	3. `item_construct_conNum.rds`

### Description
Heatmap(interactive) Correlation plot

## `plotting_descri.R`

### Data Inputs & Outputs
- Input:
	1. `psy_test_filtered.rds`,
	2. `item_construct_conNum.rds`

### Description
Visualize descriptive statistics:
1. gender ratio(pie)
2. grade composition(bar)
3. college composition(bar)
4. department composition(bar)


## `anova.R`

### Data Inputs & Outputs
- Input:
	1. `psy_test_filtered.rds`,
	2. `item_construct_conNum.rds`

